A multi-dimensional percolation approach to characterize sustainable mega-city regions

### 2018-10-17 Docs/Marami2018/Communication/marami2018.tex
slides_v1

\institute{$^{1}$Complex Systems Institute, Paris, UPS CNRS 3611 ISC-PIF\\
$^{2}$UMR CNRS 8504 G{\'e}ographie-cit{\'e}s
}

@@

$\rightarrow$ Interaction between networks and territories to capture the form-function link \cite{raimbault2018caracterisation}; potential application to sustainability of urban systems

@@

\textbf{Implementation: } construction of a single layer spatial network given the condition on the two layers and distances; extraction of connected components.

@@

\includegraphics[height=0.85\textheight]{figures/aggreg_morpho_relemissions-relefficiency_colpc1_logscale.png}

@@

\textbf{Apply to the summer school !} \texttt{https://exmodelo.org/}

@@

$\rightarrow$ Transfer to policy making recommandations: Pareto-optimal configuration can be used for the planning of regional transportation networks, subsidies policies, etc.
\smallskip

$\rightarrow$

@@

$\rightarrow$ Extrapolation of transportation flows

@@

@@

$\rightarrow$ %First step towards systematic benchmarks and multi-modeling. \textbf{Need for more systematic model exploration.} % model coupling / benchmarking

@@

$\rightarrow$ %Model integration and multi-scalarity ? \textbf{Need for more integrated models.}

@@

$\rightarrow$ %Multiple perspectives on urban systems ? \textbf{Need for more interdisciplinarity.}

@@

\textbf{Open repository} at \texttt{https://github.com/JusteRaimbault/UrbanMorphology}\\\smallskip
\textbf{Acknowledgments}: thanks to the \textit{EGI} for access to the infrastructure.

@@

\includegraphics[height=0.9\textheight]{figures/aggreg_effective.png}

>>>>

\institute{$^{1}$UPS CNRS 3611 ISC-PIF\\
$^{2}$UMR CNRS 8504 G{\'e}ographie-cit{\'e}s
}

@@

$\rightarrow$ Interactions between networks and territories to capture the link between form and function \cite{raimbault2018caracterisation}; potential application to sustainability of urban systems

@@

\textbf{Implementation: } construction of a single layer spatial network given the condition on the two layers and distances, from the 5km resolution indicators spatial field; extraction of connected components.

@@

\includegraphics[height=0.83\textheight]{figures/aggreg_morpho_relemissions-relefficiency_colpc1_logscale.png}

@@

\textbf{Apply to the summer school !} \url{https://exmodelo.org/}

@@

$\rightarrow$ Multi-dimensionality of urban systems and a link between form and function captured through multilayer percolation.
\smallskip

$\rightarrow$ Possible transfer to policy-making recommandations: Pareto-optimal configuration can be used for the planning of regional transportation networks, policies for subsidies, etc.

@@

$\rightarrow$ Systematic calibration of parameters to unveil more exhaustive Pareto fronts.

$\rightarrow$ Extrapolation of transportation flows to estimate potential emissions linked to transportation: calibration of gravity model on actual transportation emissions; use of the extrapolated parameters in potentials.

$\rightarrow$ More refined indicators for sustainability (socio-economic integration, accessibilities, different scaling exponents).
% ex : at least different scaling exponent.

@@

\vspace{-0.8cm}

@@

$\rightarrow$ Empirical and theoretical research directed towards concrete policy-making applications. \textbf{Need for more data-driven approaches.}
%First step towards systematic benchmarks and multi-modeling. \textbf{Need for more systematic model exploration.} % model coupling / benchmarking

@@

$\rightarrow$ Towards multi-scalar approaches ? \textbf{Need for more integrated models.}
 %Model integration and multi-scalarity ? \textbf{Need for more integrated models.}

@@

$\rightarrow$ Multidimensionality of urban systems ? \textbf{Need for more interdisciplinarity.}

@@

\textbf{Open repository} at \texttt{https://github.com/JusteRaimbault/UrbanMorphology} (code, data and results)%\\\smallskip

% no grid used
%\textbf{Acknowledgments}: thanks to the \textit{EGI} for access to the infrastructure.

@@

\includegraphics[height=0.83\textheight]{figures/aggreg_effective.png}
